Stack Safety as a Security Property

### 2020-06-05 main.tex
That memory layout took me more than I care to admit
Tweak to "prefix up to"

@@

\sna{This is a bit off, because \(f\) is a predicate on machine states, not the pairs (and later triples).
     Will think about what the best way is to present this.}
We will also wish to take a prefix of the trace from an initial state up through the first state where
some condition holds, using {\it split}. Let \(f\) be a predicate on machine states. Then we define
\(\mach \hookrightarrow \machT | f\) (read ``\(\machT'\) is the prefix of \(\machT\) up to \(f\)''):
  \[\frac{\mach \hookrightarrow \machT \hspace{.5cm} \mathit{split}(f,\machT) = \machT_1,\machT_2}
         {\mach \hookrightarrow \machT_1 | f}\]

@@

We also lift the prefix-up-to relation to such traces.
  \[\frac{\mpstatename \hookrightarrow \MPT \hspace{.5cm} \mathit{split}(f,\MPT) = \MPT_1,\MPT_2}
         {\mpstatename \hookrightarrow \MPT_1 | f}\]

@@

\leo{What about instructions? Shouldn't they be LC/HI?}
When \(\mpstate{\mach}{\pol}\) is a call state \(\callmap(\mach) = n\)
for some \(n\), we can construct a contour based on the bounds of the
callee's stack frame, as follows:
\leo{Should the first two cases have a $k \not \in \REGS$?}
\[\mathit{Cof}(\mach,n)(\component) =
\begin{cases}
  (\HIGHSEC,\HIGHINT) & \text{if } \component \leq \mach(\SP) - n \\
  (\HIGHSEC,\LOWINT) & \text{if } \component \geq \mach(\SP) \\
  (\LOWSEC,\LOWINT) & \text{else} \\
\end{cases}\]
%
The private state of the callee is the entire area of the memory below
the stack pointer, with the exception of the $n$ locations
corresponding to the arguments of a call. These components are tagged
high confidentiality and high integrity: the callee should be able to
neither read, nor write them.
%
Everything above the stack pointer at the point of the call is
``uninitialized'' memory that can be written into but should not be
read. To protect the callee itself from such reads, these components
are marked high confidentiality and low integrity.
%
Registers and the frame of arguments to the callee are free for the
callee to use, and are therefore tagged with low integrity and low
confidentiality.

\leo{Shouldn't this be a definition instead of a paragraph?}
%\paragraph{Integrity}

>>>>

\begin{figure}
  \begin{minipage}{\textwidth}
  \begin{center}
$\cdots$
\memory{4}{gray}%
\memory{8}{green}[{\makebox[0pt]{Caller}}]%
\memory{4}{yellow}[{\makebox[0pt]{Args}}]%
\memory{8}{red}[{\makebox[0pt]{Callee}}]%
\memory{4}{gray}%
~$\cdots$
  \end{center}
  \end{minipage}\\
~\\
~\\
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Code 1
    \end{center}
  \end{minipage}~
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Code 2
    \end{center}
  \end{minipage}
  \caption{Examples of Unsafe Programs}
  \label{fig:stackunsafety}
\end{figure}

@@

\sna{Lambdas in the split are a bit busy, not sure anything will look better.}
We will also wish to take a prefix of the trace from an initial state up through the first state where
some condition holds, using {\it split}. Let \(f\) be a predicate on machine states. Then we define
\(\mach \hookrightarrow \machT | f\) (read ``\(\machT'\) is the prefix of \(\machT\) up to \(f\)''):
  \[\frac{\mach \hookrightarrow \machT \hspace{.5cm} \mathit{split}(\lambda (\mach',\obs).f(\mach'),\machT)
            = \machT_1,\machT_2}
         {\mach \hookrightarrow \machT_1 | f}\]

@@

We also lift the prefix-up-to relation to such traces.
  \[\frac{\mpstatename \hookrightarrow \MPT \hspace{.5cm}
            \mathit{split}(\lambda \mpostate{\mach}{\pol}{\obs}.f(\mach),\MPT) = \MPT_1,\MPT_2}
         {\mpstatename \hookrightarrow \MPT_1 | f}\]

@@

\leo{What about instructions? Shouldn't they be LC/HI?}
\sna{We should consider whether applying stack safety to them is right, as
     opposed to a stronger property. Code could change instructions as long as
     they're restored before a callee returns. Shenanigans like with ROP would
     be expected.}
When \(\mpstate{\mach}{\pol}\) is a call state \(\callmap(\mach) = n\)
for some \(n\), we can construct a contour based on the bounds of the
callee's stack frame. Let \(\base \in \WORDS\) be the base of the stack,
and memory below \(\base\) set aside for code.
% Fixed. \leo{Should the first two cases have a $k \not \in \REGS$?}
\[\mathit{Cof}(\mach,n)(\component) =
\begin{cases}
  (\LOWSEC,\HIGHINT) & \text{if } \component \not \in \REGS
                       \text{ and } \component < \base \\
  (\HIGHSEC,\HIGHINT) & \text{if } \component \not \in \REGS
                        \text{ and } \base \leq \component \leq \mach(\SP) - n \\
  (\HIGHSEC,\LOWINT) & \text{if } \component \not \in \REGS
                       \text{ and } \component \geq \mach(\SP) \\
  (\LOWSEC,\LOWINT) & \text{else} \\
\end{cases}\]
The code section below the stack base is low confidentiality and high
integrity, as code should be readable but modifiable.
%
The private state of the callee is the entire area of the memory from stack
base to stack pointer, with the exception of the $n$ locations
corresponding to the arguments of a call. These components are tagged
high confidentiality and high integrity: the callee should be able to
neither read, nor write them.
%
Everything above the stack pointer at the point of the call is
``uninitialized'' memory that can be written into but should not be
read. To protect the callee itself from such reads, these components
are marked high confidentiality and low integrity.
%
Registers and the frame of arguments to the callee are free for the
callee to use, and are therefore tagged with low integrity and low
confidentiality.

%\leo{Shouldn't this be a definition instead of a paragraph?}
%\paragraph{Integrity}
